---
title: "stock_analysis"
author: "Courtney Goodridge"
date: "28/03/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

The markdown will aim to provide and working examples of the analysis and simulation of stocks. This example is taken from the following wesbite (https://towardsdatascience.com/analyzing-stocks-using-r-550be7f5f20d).

## Load packages 

```{r}
library(quantmod)
library(xts)
library(rvest)
library(tidyverse)
library(stringr)
library(forcats)
library(lubridate)
library(plotly)
library(dplyr)
library(PerformanceAnalytics)
```

```{r}
getSymbols("AMZN", from = "2008-08-01", to = "2018-08-17")

AMZN_log_returns <- AMZN %>%
  Ad()%>%
  dailyReturn(type = 'log')
```

The *getSymbols()* function selects data from a specific company stock over a specific period of time.

*Ad()* extracts open, high, low, close and volume data from the stock data object. The *dailyReturns()* then uses extracted data to calculate the daily returns. Here we specify the log of these turns. The *quantmod* package can provide different types of retruns such as weekly (*weeklyRetruns()*) or monthly (*monthlyReturns()*). 
