---
title: "stock_analysis"
author: "Courtney Goodridge"
date: "28/03/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

The markdown will aim to provide and working examples of the analysis and simulation of stocks. This example is taken from the following wesbite (https://towardsdatascience.com/analyzing-stocks-using-r-550be7f5f20d).

## Load packages 

```{r}
library(quantmod)
library(xts)
library(rvest)
library(tidyverse)
library(stringr)
library(forcats)
library(lubridate)
library(plotly)
library(dplyr)
library(PerformanceAnalytics)
```

## Selecting Amazon stock data 

```{r}
getSymbols("AMZN", from = "2008-08-01", to = "2018-08-17")

AMZN_log_returns <- AMZN %>%
  Ad()%>%
  dailyReturn(type = 'log')
```

The *getSymbols()* function selects data from a specific company stock over a specific period of time.

*Ad()* extracts open, high, low, close and volume data from the stock data object. The *dailyReturns()* then uses extracted data to calculate the daily returns. Here we specify the log of these returns. The *quantmod* package can provide different types of retruns such as weekly (*weeklyRetruns()*) or monthly (*monthlyReturns()*). 

## Plotting Amazon stock data 

```{r}
AMZN %>%
  Ad() %>% 
  chartSeries()

AMZN %>% 
  chartSeries(TA =' addBBands(); addVo(); addMACD()', subset = '2018')
```

## Plot 1: simple moving average of Amazon stock price

The first plot uses the *chartSeries()* function to plot the price of Amazon stock over the given time period. A simple moving average is used. A simple moving average is calculated by adding recent prices and then dividing by the number of time periods. For example, imagine a series of numbers (stock prices) and a fixed subset of numbers that we use to calculating the average. The first value of the moving average is calculated by taking the average of subset. The subset is then shifted forward by one number in the series, and the average calculated again - this provides the value for the second number in the moving average. 

This method can be used as finite impulse filter to smooth a signal and erradicate small flunctuations when looking at signal across large period of time (as you might be stock prices).

## Plot 2: 3 subplots containing differing types of data

*addBBands()*: This function adds Bollinger Bands to the data set. Bollinger Bands plot two lines that are 2 standard deviations (by default but this can be altered) above and below a moving average signal. Standard deviations are a measure of variability in your data - large intervals denotes increased variabilty (or volatility) of the market price, whereas lines contract when the market is less volatile.

*A brief note on Bollinger Bands*

The moving average increases towards the upper bound, traders indicate that the stock might be overbought. This can be due to market news. If this is the case, traders might bet on a reversal. If the moving average is closer to the lower bound, traders might indicate that the stock is oversold and thus is at a lower price that it's intrinsic value (https://www.investopedia.com/terms/b/bollingerbands.asp).

*addVo()*: This function plots the volume of stock traded throughout the year. As we can see, increases in volume of stock traded results in wider Bollinge Bands, indicating increased volatility.

*addMACD()*: This function plots the moving average convergence/divergence. The MACD indicator is comprised of 3 times series -  *MACD proper series* (difference between a fast expoential moving average and a slow expoential moving average), the *average signal*, and the *divergence* (difference between the two).  

An exponential moving average is where the weighting factor of the moving average decreases exponentially. This means that the greater weight is placed on more recent data points (usually measured in days) within the signal. A "fast" EMA is one where weighting is placed over a shorter amount of days, a "slow" EMA is one where the weighting is placed over a longer amount of days. The difference is the MACD signal.

When the average signal crosses the MACD series, this is an indication that the trend might be accelerating. Traders might want to buy stock when the MACD crosses above the signal line (stock is accelerating) and sell when the MACD crosses below the signal line (stock is decelerating) (https://www.investopedia.com/terms/m/macd.asp).

*Why do MACD/signal crossovers indicate traders to buy/sell*

- The fast EMA responds more quickly than the slow EMA. By comparing the differences, the MACD series can be used to indicate changes in trends of the stocks.

## Comparing public stocks

```{r}
# Facebook
getSymbols("FB", from = "2008-08-01", to = "2018-08-17")

FB_log_returns <- FB %>%
  Ad()%>%
  dailyReturn(type = 'log')

# Apple
getSymbols("AAPL", from = "2008-08-01", to = "2018-08-17")

AAPL_log_returns <- AAPL %>%
  Ad()%>%
  dailyReturn(type = 'log')

# Tesla
getSymbols("TSLA", from = "2008-08-01", to = "2018-08-17")

TSLA_log_returns <- TSLA %>%
  Ad()%>%
  dailyReturn(type = 'log')

# Google 
getSymbols("GOOGL", from = "2008-08-01", to = "2018-08-17")

GOOGL_log_returns <- GOOGL %>%
  Ad()%>%
  dailyReturn(type = 'log')

# Computing risk and reward metrics 
fb_df <- data.frame(reward = mean(FB_log_returns), risk = sd(FB_log_returns))

aapl_df <- data.frame(reward = mean(AAPL_log_returns), risk = sd(AAPL_log_returns))

tsla_df <- data.frame(reward = mean(TSLA_log_returns), risk = sd(TSLA_log_returns))

amzn_df <- data.frame(reward = mean(AMZN_log_returns), risk = sd(AMZN_log_returns))

googl_df <- data.frame(reward = mean(GOOGL_log_returns), risk = sd(GOOGL_log_returns))

df <- rbind(fb_df, aapl_df, tsla_df, amzn_df, googl_df)

df <- df %>%
  dplyr::mutate(stocks = c("FB", "AAPL", "TSLA", "AMZN", "GOOGL"))

ggplot(df, aes(x = reward, y = risk, col = stocks)) +
  geom_point()

```

This next section compares the risk and rewards of different stocks. First I load stocks from Google, Facebook, Apple, and Tesla and calculate the log retruns. The mean of the log retruns is considered the average reward for a stock. The standard deviation of the log returns can be considered the risk (i.e. highr standard deviations results in increased volatility and thus higher risk).

From this plot, we find that Google is the lowest risk but also provides the lowest return. Tesla is much more high risk but the returns are much higher. Amazon is perhaps the best middle ground providing reasonable returns with reduced risk.

## Diversifying your investments

A popular investment technique is to make your investments diverse (not putting all your eggs in one basket). 

```{r}
dat_log <-cbind(diff(log(Cl(AMZN))), diff(log(Cl(GOOGL))), diff(log(Cl(AAPL))),diff(log(Cl(FB))))

dat <- dat <-cbind(diff(Cl(AMZN)), diff(Cl(GOOGL)), diff(Cl(AAPL)), diff(Cl(FB)))

chart.Correlation(dat_log)
```
Looking at log returns, all of the correlations are significant because they are all technology companies, however the smallest correlation is between Facebook and Apple. The take home here is that you want to buy stocks that have little or no correlation the maximise the rate of return. 

*How the correlations are calculated*

He we take the closing price of each stock. We use the *diff()* function to differentiate it, thus giving use a metric for how the stock price changed.

Alternatively, the diffrence of the log can be calculated.

*Difference between the the log difference and the natural difference*

(https://money.stackexchange.com/questions/24382/what-does-the-average-log-return-value-of-a-stock-mean)

- The log return can be used as a proxy measure for the percentage change in returns between periods. However, if the market is volatile, then the log retruns will be vastly different from the percentage change.

- Conversely, just using the *diff()* function calculates the the absolute difference in returns between a given period (in this example, the difference in closing price between days).  

- If you are looking at long term investments, log returns might be best to look at as the cancel out small day-to-day fluctuations in price over long periods of time. Conversely, if investigating shorter term investments where prices changes are likely to be more volatile (over weeks/months) then utilising differences in returns or percentage differences might be better to use. 

*Other characteristics of log retruns*

- Log returns is that they are additive over time. Imagine you have a stock that increases in price of 3 periods. To calculate the one period difference between the first two periods, you would divivde the returns in period 2 by the returns in period 1. To calculate the one period difference between periods 2 and 3, you would divide the returns in period 3 by the returns in period 2.

- However if you want to the difference across multiple periods, by taking the natural log of returns you can add the percentage differences of each of the periods - this is equivalent to dividing the returns in period 3 by the retruns in period 1 (https://www.youtube.com/watch?v=PtoUlt3V0CI)